Untitled

### 2023-09-23 code/analysis_Redo.Rmd
Cleaning up the code a bit

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
```

@@

         pap.denom = pap.denom / Total * 100, 
         crc.denom = crc.denom / Total * 100, 
         adultbmi.denom = adultbmi.denom / Total * 100, 
         childbmi.denom = childbmi.denom / Total * 100, 
         htn.denom = htn.total / Total * 100, 
         dm.denom = dm.total / Total * 100) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
         PatientsPerStaff = ngla_prog_serv_revenue / Total, #Total / Staff, 
         ProgramCostPerPatient = log(ngla_expense / Total)) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Complexity, Intensity, PatientsPerStaff, ProgramCostPerPatient, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

@@

for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

>>>>

```{r}
library(readxl)
library(did2s)
library(tidyverse)
library(directlabels)
library(gtsummary)
library(kableExtra)
library(ggpubr)
```

@@

         pap.denom = pap.denom / Total * 100, 
         crc.denom = crc.denom / Total * 100, 
         adultbmi.denom = adultbmi.denom / Total * 100, 
         childbmi.denom = childbmi.denom / Total * 100, 
         htn.denom = htn.total / Total * 100, 
         dm.denom = dm.total / Total * 100) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev), 
         PatientsPerStaff = Staff, #Total / Staff, 
         ProgramCostPerPatient = log(ngla_expense / Total)) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Complexity, Intensity, PatientsPerStaff, ProgramCostPerPatient, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

@@

for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}
